Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ \smaller \textbf{{Berlin version \YellowPaperVersionNumber}}

### 2022-06-27 Paper.tex
Restrictions on r & s in ECREC precompile (#861)
* Restrictions on r & s in ECDSARECOVER precompile

* Contract s restriction between precompile and signature recovery

* Cosmetic change

* Update Paper.tex

Co-authored-by: Alex Beregszaszi <alex@rtfs.hu>

* \mathbb{B} is actually in bytes

Co-authored-by: Alex Beregszaszi <alex@rtfs.hu>
Fix: revert message should be available in the returndata buffer in case a CREATE reverts (#862)
add a link for the set of sequence of nibbles (#864)

It is defined as the function $\mathtt{HP}$ which maps from a sequence of nibbles (represented by the set $\mathbb{Y}$) together with a boolean value to a sequence of bytes (represented by the set $\mathbb{B}$):

@@

Any series of bytes may also trivially be viewed as a series of nibbles, given an endian-specific notation; here we assume big-endian. Thus:
\begin{eqnarray}
y(\mathfrak{I}) & = & \{ (\mathbf{k}_0' \in \mathbb{Y}, \mathbf{v}_0 \in \mathbb{B}), (\mathbf{k}_1' \in \mathbb{Y}, \mathbf{v}_1 \in \mathbb{B}), ... \} \\
\forall n: \quad \forall i < 2\lVert\mathbf{k}_{n}\rVert: \quad \mathbf{k}_{n}'[i] & \equiv &
\begin{cases}
\lfloor \mathbf{k}_{n}[i \div 2] \div 16 \rfloor & \text{if} \; i \; \text{is even} \\
\mathbf{k}_{n}[\lfloor i \div 2 \rfloor] \bmod 16 & \text{otherwise}
\end{cases}
\end{eqnarray}

>>>>

It is defined as the function $\mathtt{HP}$ which maps from a sequence of nibbles (represented by the set \linkdest{set_of_sequence_of_nibbles}$\mathbb{Y}$) together with a boolean value to a sequence of bytes (represented by the set $\mathbb{B}$):

@@

Any series of bytes may also trivially be viewed as a series of nibbles, given an endian-specific notation; here we assume big-endian. Thus:
\begin{eqnarray}
y(\mathfrak{I}) & = & \{ (\mathbf{k}_0' \in \hyperlink{set_of_sequence_of_nibbles}{\mathbb{Y}}, \mathbf{v}_0 \in \mathbb{B}), (\mathbf{k}_1' \in \mathbb{Y}, \mathbf{v}_1 \in \mathbb{B}), ... \} \\
\forall n: \quad \forall i < 2\lVert\mathbf{k}_{n}\rVert: \quad \mathbf{k}_{n}'[i] & \equiv &
\begin{cases}
\lfloor \mathbf{k}_{n}[i \div 2] \div 16 \rfloor & \text{if} \; i \; \text{is even} \\
\mathbf{k}_{n}[\lfloor i \div 2 \rfloor] \bmod 16 & \text{otherwise}
\end{cases}
\end{eqnarray}
